---
title: "Dev Diary - Finding Dependencies"
author: "Skyler Elmstrom"
output:
  html_document:
    code_folding: show
---

# RENV solution
RENV solution is fast, comprehensive, and actually quite useful
https://rstudio.github.io/renv/reference/dependencies.html

```{r}
renv::dependencies("../R/sortpackages.R") # clipr is the only dependency
```

BUT it doesn't really meet all of my needs. Namely:

-  It does not identify packages that are used in the script(s) but missing explicit calls in `library()` or DESCRIPTION
-  For R package code dependencies, it would be nice if the packages could be quickly added to the DESCRIPTION
-  It sometimes adds duplicates to its package list (example?)
-  The line number that the package was found would be helpful for removing/rewriting automatically later
-  An option to de-duplicate the Package list from `renv::dependencies()` would be nice

```{r}
dep <- renv::dependencies("../dev/find-dependencies/test.R")
dep$Package
```

`renv::dependencies()` calls several internal functions (which apparently can also test functions for dependencies). These functions test for R methods, `::`, `library()`, `require()`, and `requireNamespace()`. This does not check for R markdown LaTeX dependencies, but TinyTeX and Tlmgr can do a decent job of that.

```{r}
source("../R/sortpackages.R")
```

## Wrap into package list for alphabetical sorting, describing, calling

I want to use `renv::dependencies()` without the rest of the `{renv}` package... but perhaps I may just rewrite a lighterweight alternative. I think the `renv::dependencies()` output is still useful, I'd just like it to have more information.

```{r}
source("R/sortpackages.R")
dep <- renv::dependencies("dev/find-dependencies/test.R")
package_list <- dep$Package # already sorted alphabetically
```

